---
title: "R Notebook"
output: html_notebook
---

source: https://github.com/topepo/rstudio-conf-2018/tree/master/Materials

```{r}
library(tidyverse)
library(broom)
library(rsample)
library(recipes)

library(AmesHousing)
```

```{r}
ames <- make_ames()
ames %>% nrow
```

```{r}
# Make sure that you get the same random numbers
set.seed(4595)
data_split <- initial_split(ames, prop=.75, strata = "Sale_Price")

ames_train <- training(data_split)
ames_test  <- testing(data_split)

nrow(ames_train)/nrow(ames)
```

Compares train and test distributions of predicted variable

```{r}
ames_train %>% 
  ggplot(aes(x = Sale_Price)) + 
  geom_line(stat = "density", trim = TRUE) + 
  geom_line(data = ames_test, 
            stat = "density", 
            trim = TRUE, col = "red") 
```

```{r}
simple_lm <- lm(log10(Sale_Price) ~ Longitude + Latitude, data = ames_train)
simple_lm_values <- augment(simple_lm)
names(simple_lm_values)
```

```{r}
summary(simple_lm)
```

10 fold cross validation

```{r}
set.seed(2453)
cv_splits <- vfold_cv(ames_train, v = 10, strata = "Sale_Price")
cv_splits
```

The `split` objects contain the information about the sample sizes

```{r}
cv_splits$splits[[1]]
```

Use the `analysis` and `assessment` functions to get the data

```{r}
analysis(cv_splits$splits[[1]]) %>% dim()
assessment(cv_splits$splits[[1]]) %>% dim()
```

Create preprocessing recipe

```{r}
mod_rec <- recipe(Sale_Price ~ Longitude + Latitude + Neighborhood,
                  data = ames_train) %>%
  step_log(Sale_Price, base = 10) %>%
    # Lump factor levels that occur in <= 5% of data as "other"
  step_other(Neighborhood, threshold = 0.05) %>%
  # Create dummy variables for _any_ factor variables
  step_dummy(all_nominal())
```

Run the recipe

```{r}
mod_rec_trained <- prep(mod_rec, training = ames_train,
                        retain = TRUE, verbose = TRUE)
```

```{r}
mod_rec_trained
```

Apply recipe to data set ("bake" it)

```{r}
ames_test_dummies <- bake(mod_rec_trained, newdata = ames_test)
names(ames_test_dummies)
```

Non-linear relationship between price and year built

```{r}
price_breaks <- (1:6)*(10^5)

ggplot(ames_train, aes(x = Year_Built, y = Sale_Price)) + 
  geom_point(alpha = 0.4) +
    scale_x_log10() + 
  scale_y_continuous(breaks = price_breaks, trans = "log10" ) +
  geom_smooth(method = "loess")
```

Separate between airconditining or not

```{r}
library(MASS) # to get robust linear regression model, see rlm below

ggplot(ames_train, 
       aes(x = Year_Built, 
           y = Sale_Price)) + 
  geom_point(alpha = 0.4) +
  scale_y_continuous(breaks = price_breaks, 
                     trans = "log10") + 
  facet_wrap(~ Central_Air, nrow = 2) +
  geom_smooth(method = "rlm")
```

Compares plain model with one which allows for interaction between year_built and central_air

```{r}
mod1 <- lm(log10(Sale_Price) ~ Year_Built + Central_Air, data = ames_train)
mod2 <- lm(log10(Sale_Price) ~ Year_Built + Central_Air +
             Year_Built: Central_Air, data = ames_train)
anova(mod1, mod2)
```

Note: "y ~ x + y + x:y" is the same as "y ~ x * y"
source: https://www.datacamp.com/community/tutorials/r-formula-tutorial

```{r}
mod3 <- lm(log10(Sale_Price) ~ Year_Built * Central_Air, data = ames_train)
anova(mod1,mod3)
```

